---
title: "CombiningGraphs"
output: pdf_document
---

```{r}
bestcutgridfix = read.csv("../Graphs & Images/ResultsFromCutGridFixTesting/New Third Test - MMR/2019-07-16AverageHolder.csv")
bestfullgridfix = read.csv("../Graphs & Images/ResultsFromFullGridFixTesting/New Fifth Test - MMR/2019-07-17AverageHolder.csv")
bestcutrandom = read.csv("../Graphs & Images/ResultsFromCutRandomTesting/CutRandom_2019-07-17AverageHolder.csv")
bestfullrandom = read.csv("../Graphs & Images/ResultsFromFullRandomTesting/FullRandom_2019-07-16AverageHolder.csv")
besttemporal = read.csv("../Graphs & Images/ResultsfromTemporalShift/New First Test - MMR/2019-07-17AverageHolder.csv")
bestspatial = read.csv("../Graphs & Images/ResultsfromSpatialShift/New Fifth Test - MMR/2019-07-18AverageHolder.csv")
```


##Train Accuracy
```{r}
# png("../Graphs & Images/Basic Layouts/ModelTrainingAcc.png", width=8,height=6,units='in', res=600)
plot(bestcutgridfix$Train_Acc, type="l", ylim=c(55,100),col='purple', lwd=2, ylab="Accuracy", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Training Accuracy")
lines(bestfullgridfix$Train_Acc, col='blue', lwd=2)
lines(bestcutrandom$Train_Acc, col='cyan', lwd=2)
lines(bestfullrandom$Train_Acc, col='green', lwd=2)
lines(besttemporal$Train_Acc, col='orange', lwd=2)
lines(bestspatial$Train_Acc, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), fill=c('purple','blue','cyan','green','orange','red'))
# dev.off()
```
##Testing Accuracy
```{r}
png("../Graphs & Images/Basic Layouts/ModelTestingAcc.png", width=8,height=6,units='in', res=600)
plot(bestcutgridfix$Test_Acc, type="l", ylim=c(55,100),col='purple', lwd=2, ylab="Accuracy", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Testing Accuracy")
lines(bestfullgridfix$Test_Acc, col='blue', lwd=2)
lines(bestcutrandom$Test_Acc, col='cyan', lwd=2)
lines(bestfullrandom$Test_Acc, col='green', lwd=2)
lines(besttemporal$Test_Acc, col='orange', lwd=2)
lines(bestspatial$Test_Acc, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), fill=c('purple','blue','cyan','green','orange','red'))
dev.off()
```

#Training Loss
```{r}
png("../Graphs & Images/Basic Layouts/ModelTrainingLoss.png", width=8,height=6,units='in', res=600)
plot(bestcutgridfix$Train_Loss, type="l", ylim=c(0,.1),col='purple', lwd=2, ylab="Loss", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Model Training Loss")
lines(bestfullgridfix$Train_Loss, col='blue', lwd=2)
lines(bestcutrandom$Train_Loss, col='cyan', lwd=2)
lines(bestfullrandom$Train_Loss, col='green', lwd=2)
lines(besttemporal$Train_Loss, col='orange', lwd=2)
lines(bestspatial$Train_Loss, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("topright",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), fill=c('purple','blue','cyan','green','orange','red'))
dev.off()
```

#Testing Loss
```{r}
png("../Graphs & Images/Basic Layouts/ModelTestingLoss.png", width=8,height=6,units='in', res=600)
plot(bestcutgridfix$Test_Loss, type="l", ylim=c(0,.25),col='purple', lwd=2, ylab="Loss", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Model Testing Loss")
lines(bestfullgridfix$Test_Loss, col='blue', lwd=2)
lines(bestcutrandom$Test_Loss, col='cyan', lwd=2)
lines(bestfullrandom$Test_Loss, col='green', lwd=2)
lines(besttemporal$Test_Loss, col='orange', lwd=2)
lines(bestspatial$Test_Loss, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("topleft",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), fill=c('purple','blue','cyan','green','orange','red'))
dev.off()
```

##Ratio Split Versions Import
```{r}
spatialonefourth = read.csv("../Graphs & Images/ResultsfromSpatialShift/75-25 Split/2019-07-19AverageHolder.csv")
spatialonehalf = read.csv("../Graphs & Images/ResultsfromSpatialShift/50-50 Split/2019-07-19AverageHolder.csv")
temporalonefourth = read.csv("../Graphs & Images/ResultsfromTemporalShift/75-25 Split/2019-07-19AverageHolder.csv")
temporalonehalf = read.csv("../Graphs & Images/ResultsfromTemporalShift/50-50 Split/2019-07-19AverageHolder.csv")
fullgridfixonefourth = read.csv("../Graphs & Images/ResultsFromFullGridFixTesting/75-25 Split/2019-07-19AverageHolder.csv")
fullgridfixonehalf = read.csv("../Graphs & Images/ResultsFromFullGridFixTesting/50-50 Split/2019-07-19AverageHolder.csv")
cutgridfixonefourth = read.csv("../Graphs & Images/ResultsFromCutGridFixTesting/75-25 Split/2019-07-19AverageHolder.csv")
cutgridfixonehalf = read.csv("../Graphs & Images/ResultsFromCutGridFixTesting/50-50 Split/2019-07-19AverageHolder.csv")
fullrandomonefourth = read.csv("../Graphs & Images/ResultsFromFullRandomTesting/FullRandom-75-25-2019-07-17AverageHolder.csv")
fullrandomonehalf = read.csv("../Graphs & Images/ResultsFromFullRandomTesting/FullRandom-50-50-2019-07-17AverageHolder.csv")
cutrandomonefourth = read.csv("../Graphs & Images/ResultsFromCutRandomTesting/CutRandom-75-25-2019-07-19AverageHolder.csv")
cutrandomonehalf = read.csv("../Graphs & Images/ResultsFromCutRandomTesting/CutRandom-50-50-2019-07-19AverageHolder.csv")
```

##Train Accuracy
```{r}
png("../Graphs & Images/Basic Layouts/RatioModelTrainingAcc.png", width=8,height=6,units='in', res=600)
par(mar=c(4, 4, 3, 10))
plot(cutgridfixonefourth$Train_Acc, type="l", ylim=c(70,95),col='purple', lwd=2, ylab="Accuracy", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Training Accuracy, Ratio Models")
lines(cutgridfixonehalf$Train_Acc, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$Train_Acc, col='blue', lwd=2)
lines(fullgridfixonehalf$Train_Acc, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$Train_Acc, col='cyan', lwd=2)
lines(cutrandomonehalf$Train_Acc, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$Train_Acc, col='green', lwd=2)
lines(fullrandomonehalf$Train_Acc, col='green', lwd=2, lty=3)
lines(temporalonefourth$Train_Acc, col='orange', lwd=2)
lines(temporalonehalf$Train_Acc, col='orange', lwd=2, lty=3)
lines(spatialonefourth$Train_Acc, col='red', lwd=2)
lines(spatialonehalf$Train_Acc, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,.1), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, xpd=TRUE)
dev.off()
```
##Testing Accuracy
```{r}
png("../Graphs & Images/Basic Layouts/RatioModelTestingAcc.png", width=8,height=6,units='in', res=600)
par(mar=c(4, 4, 3, 10))
plot(cutgridfixonefourth$Test_Acc, type="l", ylim=c(70,95),col='purple', lwd=2, ylab="Accuracy", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Testing Accuracy, Ratio Models")
lines(cutgridfixonehalf$Test_Acc, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$Test_Acc, col='blue', lwd=2)
lines(fullgridfixonehalf$Test_Acc, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$Test_Acc, col='cyan', lwd=2)
lines(cutrandomonehalf$Test_Acc, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$Test_Acc, col='green', lwd=2)
lines(fullrandomonehalf$Test_Acc, col='green', lwd=2, lty=3)
lines(temporalonefourth$Test_Acc, col='orange', lwd=2)
lines(temporalonehalf$Test_Acc, col='orange', lwd=2, lty=3)
lines(spatialonefourth$Test_Acc, col='red', lwd=2)
lines(spatialonehalf$Test_Acc, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,.1), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, xpd=TRUE)
dev.off()
```

#Testing Loss
```{r}
png("../Graphs & Images/Basic Layouts/RatioModelTestingLoss.png", width=8,height=6,units='in', res=600)
par(mar=c(4, 4, 3, 10))
plot(cutgridfixonefourth$Test_Loss, type="l", ylim=c(0,.25),col='purple', lwd=2, ylab="Loss", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Training Loss, Ratio Models")
lines(cutgridfixonehalf$Test_Loss, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$Test_Loss, col='blue', lwd=2)
lines(fullgridfixonehalf$Test_Loss, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$Test_Loss, col='cyan', lwd=2)
lines(cutrandomonehalf$Test_Loss, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$Test_Loss, col='green', lwd=2)
lines(fullrandomonehalf$Test_Loss, col='green', lwd=2, lty=3)
lines(temporalonefourth$Test_Loss, col='orange', lwd=2)
lines(temporalonehalf$Test_Loss, col='orange', lwd=2, lty=3)
lines(spatialonefourth$Test_Loss, col='red', lwd=2)
lines(spatialonehalf$Test_Loss, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,.1), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, xpd=TRUE)
dev.off()
```

#Training Loss
```{r}
png("../Graphs & Images/Basic Layouts/RatioModelTrainingLoss.png", width=8,height=6,units='in', res=600)
par(mar=c(4, 4, 3, 10))
plot(cutgridfixonefourth$Train_Loss, type="l", ylim=c(0,.25),col='purple', lwd=2, ylab="Loss", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Training Loss, Ratio Models")
lines(cutgridfixonehalf$Train_Loss, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$Train_Loss, col='blue', lwd=2)
lines(fullgridfixonehalf$Train_Loss, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$Train_Loss, col='cyan', lwd=2)
lines(cutrandomonehalf$Train_Loss, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$Train_Loss, col='green', lwd=2)
lines(fullrandomonehalf$Train_Loss, col='green', lwd=2, lty=3)
lines(temporalonefourth$Train_Loss, col='orange', lwd=2)
lines(temporalonehalf$Train_Loss, col='orange', lwd=2, lty=3)
lines(spatialonefourth$Train_Loss, col='red', lwd=2)
lines(spatialonehalf$Train_Loss, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,.1), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, xpd=TRUE)
dev.off()
```

```{r}
cutgridfixonefourth$Total = cutgridfixonefourth$FN + cutgridfixonefourth$TP
cutgridfixonehalf$Total = cutgridfixonehalf$FN + cutgridfixonehalf$TP

fullgridfixonefourth$Total = fullgridfixonefourth$FN + fullgridfixonefourth$TP
fullgridfixonehalf$Total = fullgridfixonehalf$FN +  fullgridfixonehalf$TP

cutrandomonefourth$Total = cutrandomonefourth$FN + cutrandomonefourth$TP
cutrandomonehalf$Total = cutrandomonehalf$FN + cutrandomonehalf$TP

fullrandomonefourth$Total = fullrandomonefourth$FN + fullrandomonefourth$TP
fullrandomonehalf$Total = fullrandomonehalf$FN + fullrandomonehalf$TP

fullrandomonefourth$Total = fullrandomonefourth$FN + fullrandomonefourth$TP
fullrandomonehalf$Total = fullrandomonehalf$FN + fullrandomonehalf$TP

spatialonefourth$Total = spatialonefourth$FN + spatialonefourth$TP
spatialonehalf$Total = spatialonehalf$FN + spatialonehalf$TP

temporalonefourth$Total = temporalonefourth$FN + temporalonefourth$TP
temporalonehalf$Total = temporalonehalf$FN + temporalonehalf$TP

##Best tests
bestcutgridfix$Total = bestcutgridfix$FN + bestcutgridfix$TP
bestfullgridfix$Total = bestfullgridfix$FN + bestfullgridfix$TP
bestcutrandom$Total = bestcutrandom$FN + bestcutrandom$TP
bestfullrandom$Total = bestfullrandom$FN + bestfullrandom$TP

besttemporal$Total = besttemporal$FN + besttemporal$TP
bestspatial$Total = bestspatial$FN + bestspatial$TP

```


#Percent Correct Accident Records - Ratio Models
```{r}
png("../Graphs & Images/Basic Layouts/RatioModelAccidentCorrect.png", width=6,height=3,units='in', res=600)
par(mar=c(4, 4, 2, 8))
plot(cutgridfixonefourth$TP/cutgridfixonefourth$Total, type="l", ylim=c(0,1),col='purple', lwd=2, ylab="Percent Correct", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Ratio Models - Accidents Correct")
lines(cutgridfixonehalf$TP/cutgridfixonehalf$Total, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$TP/fullgridfixonefourth$Total, col='blue', lwd=2)
lines(fullgridfixonehalf$TP/fullgridfixonehalf$Total, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$TP/cutrandomonefourth$Total, col='cyan', lwd=2)
lines(cutrandomonehalf$TP/cutrandomonehalf$Total, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$TP/fullrandomonefourth$Total, col='green', lwd=2)
lines(fullrandomonehalf$TP/fullrandomonehalf$Total, col='green', lwd=2, lty=3)
lines(temporalonefourth$TP/temporalonefourth$Total, col='orange', lwd=2)
lines(temporalonehalf$TP/temporalonehalf$Total, col='orange', lwd=2, lty=3)
lines(spatialonefourth$TP/spatialonefourth$Total, col='red', lwd=2)
lines(spatialonehalf$TP/spatialonehalf$Total, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,0), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, xpd=TRUE, cex=0.75)
dev.off()
```

#Accidents Correct - Best Models
```{r}
png("../Graphs & Images/Basic Layouts/ModelCorrect.png", width=6,height=6,units='in', res=600)
par(mfrow = c( 2, 1 ), mar=c(3, 4, 1, 6))
plot(bestcutgridfix$TP/bestcutgridfix$Total, type="l", ylim=c(0,1),col='purple', lwd=2, ylab="Percent Correct", xlab="", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Test Models - Accidents Correct")
# lines(bestcutgridfix$TP/bestcutgridfix$Total, col='purple', lwd=2)
lines(bestfullgridfix$TP/bestfullgridfix$Total, col='blue', lwd=2)
lines(bestcutrandom$TP/bestcutrandom$Total, col='cyan', lwd=2)
lines(bestfullrandom$TP/bestfullrandom$Total, col='green', lwd=2)
lines(besttemporal$TP/besttemporal$Total, col='orange', lwd=2)
lines(bestspatial$TP/bestspatial$Total, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")


plot(bestcutgridfix$TN/bestcutgridfix$Total0, type="l", ylim=c(0.55,1),col='purple', lwd=2, ylab="Percent Correct", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Test Models - Negatives Correct")
# lines(bestcutgridfix$TN/bestcutgridfix$Total0, col='purple', lwd=2)
lines(bestfullgridfix$TN/bestfullgridfix$Total0, col='blue', lwd=2)
lines(bestcutrandom$TN/bestcutrandom$Total0, col='cyan', lwd=2)
lines(bestfullrandom$TN/bestfullrandom$Total0, col='green', lwd=2)
lines(besttemporal$TN/besttemporal$Total0, col='orange', lwd=2)
lines(bestspatial$TN/bestspatial$Total0, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
par(xpd=NA)
legend("topleft",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), col=c('purple','blue','cyan','green','orange','red'), seg.len = 1, inset=c(1,-0.4), cex=0.75, lty="solid")

dev.off()
```




##AUC Curve for Models 
```{r}
png("../Graphs & Images/Basic Layouts/ModelAUC.png", width=8,height=6,units='in', res=600)
par(mar=c(4, 4, 3, 8))
plot(bestcutgridfix$AUC, type="l", ylim=c(.5,1),col='purple', lwd=2, ylab="AUC Score", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Model AUC Comparison")
# lines(bestcutgridfix$AUC, col='purple', lwd=2)
lines(bestfullgridfix$AUC, col='blue', lwd=2)
lines(bestcutrandom$AUC, col='cyan', lwd=2)
lines(bestfullrandom$AUC, col='green', lwd=2)
lines(besttemporal$AUC, col='orange', lwd=2)
lines(bestspatial$AUC, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomright",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), fill=c('purple','blue','cyan','green','orange','red'), seg.len = 1)
# xpd=TRUE, inset=c(1,.1))
dev.off()
```

##AUC For Ratios
```{r}
png("../Graphs & Images/Basic Layouts/RatioAUC.png", width=8,height=6,units='in', res=600)
par(mar=c(4, 4, 3, 10))
plot(cutgridfixonefourth$AUC, type="l", ylim=c(0.69,1),col='purple', lwd=2, ylab="AUC Score", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Ratio Model AUC Comparison")
lines(cutgridfixonehalf$AUC, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$AUC, col='blue', lwd=2)
lines(fullgridfixonehalf$AUC, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$AUC, col='cyan', lwd=2)
lines(cutrandomonehalf$AUC, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$AUC, col='green', lwd=2)
lines(fullrandomonehalf$AUC, col='green', lwd=2, lty=3)
lines(temporalonefourth$AUC, col='orange', lwd=2)
lines(temporalonehalf$AUC, col='orange', lwd=2, lty=3)
lines(spatialonefourth$AUC, col='red', lwd=2)
lines(spatialonehalf$AUC, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,.1), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, xpd=TRUE)
dev.off()
```

##Percent 0 correct
```{r}
cutgridfixonefourth$Total0 = cutgridfixonefourth$FP + cutgridfixonefourth$TN
cutgridfixonehalf$Total0 = cutgridfixonehalf$FP + cutgridfixonehalf$TN

fullgridfixonefourth$Total0 = fullgridfixonefourth$FP + fullgridfixonefourth$TN
fullgridfixonehalf$Total0 = fullgridfixonehalf$FP +  fullgridfixonehalf$TN

cutrandomonefourth$Total0 = cutrandomonefourth$FP + cutrandomonefourth$TN
cutrandomonehalf$Total0 = cutrandomonehalf$FP + cutrandomonehalf$TN

fullrandomonefourth$Total0 = fullrandomonefourth$FP + fullrandomonefourth$TN
fullrandomonehalf$Total0 = fullrandomonehalf$FP + fullrandomonehalf$TN

fullrandomonefourth$Total0 = fullrandomonefourth$FP + fullrandomonefourth$TN
fullrandomonehalf$Total0 = fullrandomonehalf$FP + fullrandomonehalf$TN

spatialonefourth$Total0 = spatialonefourth$FP + spatialonefourth$TN
spatialonehalf$Total0 = spatialonehalf$FP + spatialonehalf$TN

temporalonefourth$Total0 = temporalonefourth$FP + temporalonefourth$TN
temporalonehalf$Total0 = temporalonehalf$FP + temporalonehalf$TN

##Best tests
bestcutgridfix$Total0 = bestcutgridfix$FP + bestcutgridfix$TN
bestfullgridfix$Total0 = bestfullgridfix$FP + bestfullgridfix$TN
bestcutrandom$Total0 = bestcutrandom$FP + bestcutrandom$TN
bestfullrandom$Total0 = bestfullrandom$FP + bestfullrandom$TN

besttemporal$Total0 = besttemporal$FP + besttemporal$TN
bestspatial$Total0 = bestspatial$FP + bestspatial$TN

```

#Percent Correct Negatives Records - Ratio Models
```{r}
png("../Graphs & Images/Basic Layouts/RatioModelsCorrect.png", width=6,height=6,units='in', res=600)
par(mfrow = c( 2, 1 ),mar=c(2.5, 4, 1, 8))

plot(cutgridfixonefourth$TP/cutgridfixonefourth$Total, type="l", ylim=c(0,1),col='purple', lwd=2, ylab="Percent Correct", xlab="", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Ratio Models - Accidents Correct")
lines(cutgridfixonehalf$TP/cutgridfixonehalf$Total, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$TP/fullgridfixonefourth$Total, col='blue', lwd=2)
lines(fullgridfixonehalf$TP/fullgridfixonehalf$Total, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$TP/cutrandomonefourth$Total, col='cyan', lwd=2)
lines(cutrandomonehalf$TP/cutrandomonehalf$Total, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$TP/fullrandomonefourth$Total, col='green', lwd=2)
lines(fullrandomonehalf$TP/fullrandomonehalf$Total, col='green', lwd=2, lty=3)
lines(temporalonefourth$TP/temporalonefourth$Total, col='orange', lwd=2)
lines(temporalonehalf$TP/temporalonehalf$Total, col='orange', lwd=2, lty=3)
lines(spatialonefourth$TP/spatialonefourth$Total, col='red', lwd=2)
lines(spatialonehalf$TP/spatialonehalf$Total, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")

plot(cutgridfixonefourth$TN/cutgridfixonefourth$Total0, type="l", ylim=c(0.73,1),col='purple', lwd=2, ylab="Percent Correct", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Ratio Models - Negatives Correct")
lines(cutgridfixonehalf$TN/cutgridfixonehalf$Total0, col='purple', lwd=2, lty=3)
lines(fullgridfixonefourth$TN/fullgridfixonefourth$Total0, col='blue', lwd=2)
lines(fullgridfixonehalf$TN/fullgridfixonehalf$Total0, col='blue', lwd=2, lty=3)
lines(cutrandomonefourth$TN/cutrandomonefourth$Total0, col='cyan', lwd=2)
lines(cutrandomonehalf$TN/cutrandomonehalf$Total0, col='cyan', lwd=2, lty=3)
lines(fullrandomonefourth$TN/fullrandomonefourth$Total0, col='green', lwd=2)
lines(fullrandomonehalf$TN/fullrandomonehalf$Total0, col='green', lwd=2, lty=3)
lines(temporalonefourth$TN/temporalonefourth$Total0, col='orange', lwd=2)
lines(temporalonehalf$TN/temporalonehalf$Total0, col='orange', lwd=2, lty=3)
lines(spatialonefourth$TN/spatialonefourth$Total0, col='red', lwd=2)
lines(spatialonehalf$TN/spatialonehalf$Total0, col='red', lwd=2, lty=3)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")

par(xpd=NA)
legend("bottomleft",c('Cut GridFix 75-25', 'Cut GridFix 50-50','Full GridFix 75-25','Full GridFix 50-50', 'Cut Random 75-25','Cut Random 50-50','Full Random 75-25','Full Random 50-50', 'Temporal 75-25','Temporal 50-50', 'Spatial 75-25', 'Spatial 50-50'),col=c('purple','purple','blue','blue', 'cyan','cyan','green','green','orange','orange', 'red','red'), inset=c(1,.8), lty=c("solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed","solid","dashed"), seg.len = 1, cex=0.75)



dev.off()
```


#Negatives Correct - Best Models
```{r}
png("../Graphs & Images/Basic Layouts/ModelNegativeCorrect.png", width=6,height=3,units='in', res=600)
par(mar=c(4, 4, 2, 6))
plot(bestcutgridfix$TN/bestcutgridfix$Total0, type="l", ylim=c(0.55,1),col='purple', lwd=2, ylab="Percent Correct", xlab="Model Cycle", xlim=c(.5,50.5), xaxt="none", yaxt="none",main="Negatives Correct")
# lines(bestcutgridfix$TN/bestcutgridfix$Total0, col='purple', lwd=2)
lines(bestfullgridfix$TN/bestfullgridfix$Total0, col='blue', lwd=2)
lines(bestcutrandom$TN/bestcutrandom$Total0, col='cyan', lwd=2)
lines(bestfullrandom$TN/bestfullrandom$Total0, col='green', lwd=2)
lines(besttemporal$TN/besttemporal$Total0, col='orange', lwd=2)
lines(bestspatial$TN/bestspatial$Total0, col='red', lwd=2)
axis(1, seq(0,50,by=5), seq(0,50,by=5),las="2")
axis(2,las="2")
legend("topleft",c('Cut GridFix', 'Full GridFix','Cut Random','Full Random','Temporal','Spatial'), col=c('purple','blue','cyan','green','orange','red'), seg.len = 1, xpd=TRUE, inset=c(1,.1), cex=0.75, lty="solid")
dev.off()
```